Self Regulation Ontology Retest Data Report

### 2017-04-17 SRO_Report.Rmd
fixed completion times plots

```{r}
rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data)
```

@@

Median reliability and the number of variables for both the surveys and the tasks:
As implied by Spearman the ICC's are higher for surveys.  
Systematic differences between the two measurements are higher for tasks than surveys (potentially indicating learning effects).  
Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
```{r}
icc_df %>%
  group_by(task) %>%
  summarise(median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```

@@

```{r}
t1_2_difference = data.frame()

@@

str(as.data.frame(t1_2_difference$difference))
```

@@

```{r}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)

t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
```

@@

```{r}
tmp = t1_2_difference %>%
  group_by(sub_id) %>%
  summarise(mean_diff = mean(difference, na.rm=T),
            days_btw = unique(days_btw))

length(unique(tmp$mean_diff))
str(as.data.frame(t1_2_difference$difference))

tmp %>%
  ggplot(aes(days_btw, mean_diff))+
  geom_point()+
  theme_bw()
```

@@

```{r}
t1_2_difference %>%
  ggplot(aes(dv, difference))+
  geom_boxplot()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

>>>>

```{r}
rm(hddm_refits, transformed_hddm_refits, hddm_logTr_vars, transform_hddm_logTr_vars, replace_hddm_vars, hddm_fix_retest_subs_test_data, sign, i)
```

@@

Median reliability and the number of variables for both the surveys and the tasks:
As seen with Spearman $\rho$'s as well the ICC's are higher for surveys.  
Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
```{r}
icc_df %>%
  group_by(task) %>%
  summarise(median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```

@@

```{r warning=FALSE}
t1_2_difference = data.frame()

@@

t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
```

```{r echo=FALSE}
rm(tmp, i)
```

@@

```{r warning=FALSE}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)

t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
str(t1_2_difference)
```

@@

```{r warning=FALSE, message=FALSE}
tmp = t1_2_difference %>%
  group_by(sub_id) %>%
  summarise(mean_diff = mean(difference, na.rm=T),
            days_btw = unique(days_btw))

ggplotly(tmp %>%
  ggplot(aes(days_btw, mean_diff))+
  geom_point()+
  theme_bw()+
  xlab("Days between completion")+
  ylab("Mean standardized difference between two time points")+
  geom_smooth(method="lm"))
```

@@

```{r fig.width=20}
t1_2_difference %>%
  ggplot(aes(dv, difference))+
  geom_boxplot()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
